An Executable Formal Semantics For A Functional Actor Language

### 2017-12-20 paper/paper.tex
conclusion section

\subsection{Configuration}
All languages in K use a configuration to specify the current state of a
program. For simple languages like the lambda calculus or a simple \texttt{IMP}
language, there may only be one cell to hold the current computation (the
\texttt{k} cell) and perhaps another \texttt{env} cell for the current
environment. For the actor language, we have the following configuration:
\begin{verbatim}
configuration 
  <T>
    <actors>
      <actor multiplicity="*">     // a multiset of actors
        <k> exec($PGM:Exp) </k>    // actor state
        <id> initactor </id>       // actor id
      </actor>
    </actors>
    <messages>
      <message  multiplicity="*">  // a multiset of messages
        .K
      </message>
    </messages>
    <definedaddr>                  // list of defined actors'
      ListItem(initactor)          // addresses
    </definedaddr>
  </T>
\end{verbatim}
In addition to defining the state of a program, the configuration is also used
to define the initial state of a program. Initially, we only have one actor,
with the unique identifier \texttt{initactor}. It also contains the program in
the \texttt{exec} state ready to be executed. The variable \texttt{\$PGM} comes
from an external file. The notation \texttt{multiplicity=*} is used to specify
that there can be any number of \texttt{actor} cells and \texttt{message} cells
as a multiset of actors and messages respectively. Initially there are no
messages, represented using K's builtin \texttt{.K}. Finally, the
\texttt{definedaddr} cell is used to keep track of addresses of defined
actors. We need to keep track of this for the side condition of some semantic
rules (see Section~\ref{sec:semantics}).

@@

Another area for future work inovlves extending

Finally, an important area for future work involves taking advantage of K's
backend tools for formal analysis, such as proving actor programs correct using
K's verification engine. For verification, K uses reachability logic~\cite{}, a
language-independent formal verification framework. Reachability logic supports
all-path reachability, so it can be used to verify programs involving concurrent
semantics. However, in order to fully take advantage of this verification, one
would need to implement partial-order reduction in K in order to reduce the
state space.

>>>>

\subsection{Configuration}\label{sec:configuration}
All languages in K use a configuration to specify the current state of a
program. For simple languages like the lambda calculus or a simple \texttt{IMP}
language, there may only be one cell to hold the current computation (the
\texttt{<k>}\ \dots\ \texttt{</k>} cell) which is required for all languages
defined in K. For the actor language, we have the following configuration:
\begin{verbatim}
configuration 
  <T>
    <actors>
      <actor multiplicity="*">     // a multiset of actors
        <k> exec($PGM:Exp) </k>    // actor state
        <id> initactor </id>       // actor id
      </actor>
    </actors>
    <messages>
      <message  multiplicity="*">  // a multiset of messages
        .K
      </message>
    </messages>
    <definedaddr>                  // list of defined actors'
      ListItem(initactor)          // addresses
    </definedaddr>
  </T>
\end{verbatim}
In addition to defining the state of a program, the configuration is also used
to define the initial state of a program. Initially, we only have one actor,
with the unique identifier \texttt{initactor}. It also contains the program in
the \texttt{exec} state ready to be executed. The variable \texttt{\$PGM} comes
from an external file. The notation \texttt{multiplicity=*} is used to specify
that there can be any number of \texttt{actor} cells and \texttt{message} cells
as a multiset of actors and messages respectively. Initially there are no
messages, represented using K's builtin \texttt{.K}. Finally, the
\texttt{definedaddr} cell is used to keep track of addresses of defined
actors. We need to keep track of this for the side condition of some semantic
rules (see Section~\ref{sec:semantics}).

@@

Another important area for future work involves taking advantage of K's
backend tools for formal analysis, such as proving actor programs correct using
K's verification engine. For verification, K uses reachability logic~\cite{}, a
language-independent formal verification framework. Reachability logic supports
all-path reachability, so it can be used to verify programs involving concurrent
semantics. However, in order to fully take advantage of this verification, one
would need to implement partial-order reduction in K in order to reduce the
state space.

Finally, we would also like to extend our semantics to allow interaction between
actor systems by adding external actors and receptionists, as mentioned in
Section~\ref{sec:configuration}. This would allow us to define more complicated
programs, and it would also allow us to define programs like the tree product
program more compactly. Additionally, it would allow us to begin asking
questions regarding observational equivalence of actor systems, and perhaps even
take advantage of K's analysis tools to prove such equivalences.
